Fermi and eROSITA bubbles

### 2021-11-08 paper.tex
update

\subsection{X-ray and Gamma-ray emission}
  \begin{enumerate}
    \item X-ray:
       \begin{enumerate}
         \item Thermal bremsstrahlung: The X-ray emissivity in an energy range 1.4–1.6 keV is calculated\
               using the MEKAL model (\citealt{Xray-1}; \citealt{Xray-2}; \citealt{Xray-3})\
               implemented in the utility XSPEC\citep{XSPEC}, assuming solar metallicity.
       \end{enumerate}
    \item Gamma-ray:
       \begin{enumerate}
         \item Leptonic process:\\
          The gamma-ray emission is produced by inverse Comptom scattering of the ISRF by CRe.
         \item Hadronic process:\\
          In the hadronic model, CRp undergo hadronic collisions with thermal gas protons\
          and produce $\gamma$-ray via pion decay. The volume emissivity of the emission can be writen as
          \begin{equation}
             \epsilon \propto U_{\text{CRp}}n_{p}\sigma_{p}\kappa_{pp}.
          \end{equation}
       \end{enumerate}
  \end{enumerate}

>>>>

\subsection{X-ray and Gamma-ray emission}
  \begin{enumerate}
    \item X-ray:
       \begin{enumerate}
         \item Thermal bremsstrahlung: The X-ray emissivity in an energy range 1.4–1.6 keV is calculated\
               using the MEKAL model (\citealt{Xray-1}; \citealt{Xray-2}; \citealt{Xray-3})\
               implemented in the utility XSPEC\citep{XSPEC}, assuming solar metallicity.
       \end{enumerate}
    \item Gamma-ray:
       \begin{enumerate}
         \item Leptonic process:\\
          The gamma-ray emission is produced by inverse Comptom scattering of the ISRF by CRe.
         \item Hadronic process:\\
          In the hadronic model, CRp undergo hadronic collisions with thermal gas protons\
          and produce $\gamma$-ray via pion decay. The volume emissivity of the emission can be written as
          \begin{equation}
             \epsilon \propto U_{\text{CRp}}n_{p}\sigma_{p}\kappa_{pp}.
          \end{equation}
       \end{enumerate}
  \end{enumerate}

Note that the observed X-ray emission is contributed by all the gas in the Milky Way halo,\
which likely extends to a radius of $\sim$250 kpc (\citealt{halo-radius-1}; \citealt{halo-radius-2}),\
much bigger than our simulation box. Therefore, we first compute the X-ray emissivity\
from the simulated gas within a radius of 25 kpc away from the GC.
Then, beyond 25 kpc the gas is assumed to be isothermal with $T=10^6$ K and\
follows out to a radius of 250 kpc the observed density profile of \citep{temperature-MW}.
